\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-04-21 investigation/docs/overview.tex
edits to varioys code and report docs

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
 probename & snp1 & snp2 & gene & meanlambda & npairs \\ 
  \hline
ILMN\_1704730 & rs1884655 & rs10255470 & CD93 & 2.88 & 10 \\ 
ILMN\_1710752 & rs2123758 & rs2786014 & NAPRT1 & 2.15 & 8 \\ 
ILMN\_1717234 & rs1157079 & rs7733671 & CAST & 4.31 & 17 \\ 
ILMN\_1720059 & rs12435486 & rs7837237 & HMBOX1 & 2.29 & 7 \\ 
ILMN\_1738784 & rs10930170 & rs12120009 & PPP2R5A & 2.24 & 6 \\ 
ILMN\_1755589 & rs11080134 & rs11169322 & DIP2B & 1.16 & 6 \\ 
ILMN\_1786426 & rs2839013 & rs8106959 & TMEM149 & 5.65 & 20 \\ 
ILMN\_1804396 & rs1293455 & rs2655991 & C14ORF4 & 1.38 & 7 \\ 
ILMN\_2313158 & rs10869600 & rs13069559 & MBNL1 & 3.15 & 15 \\ 
ILMN\_2372639 & rs17159840 & rs10059004 & TRAPPC5 & 4.17 & 17 \\ 
ILMN\_3231952 & rs12947580 & rs8079215 & ARL17B & 2.16 & 6 \\ 
   \hline
\end{tabular}
\caption*{Mean lambda per probe, when 5 or more interactions are identified amongst the 501 pairs}
\end{table}

@@

2. Identify the largest additive eQTL for the probe (irrespective of effect size). Regress out the effect of the additive loci and use the adjusted phenotype for 8df and 4df model analysis. Results reported are the 8df and 4df of original pair and the empirical p-values from genome-wide analysis fitting each of the two SNPs as fixed. As before these are determined by filtering out the SNPs on the same chromosome as the original fixed SNP and also within +/- 5MB of the second SNP. \\

[Currently running]

2. Prediction \\

Of the 501 SNP pairs, 484 have both SNP in the EGCUT data. Most of the Inchianti SNPs need to be imputed, but we expect most to pass filtering. For pairs without and Inchianti SNP I propose using the SNP with the largest additive effect in the egcut data. \\

@@

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
 probename & snp1 & snp2 & gene & meanlambda & npairs \\ 
  \hline
ILMN\_1704730 & rs1884655 & rs10255470 & CD93 & 2.88 & 10 \\ 
ILMN\_1710752 & rs2123758 & rs2786014 & NAPRT1 & 2.15 & 8 \\ 
ILMN\_1717234 & rs1157079 & rs7733671 & CAST & 4.31 & 17 \\ 
ILMN\_1720059 & rs12435486 & rs7837237 & HMBOX1 & 2.29 & 7 \\ 
ILMN\_1738784 & rs10930170 & rs12120009 & PPP2R5A & 2.24 & 6 \\ 
ILMN\_1755589 & rs11080134 & rs11169322 & DIP2B & 1.16 & 6 \\ 
ILMN\_1786426 & rs2839013 & rs8106959 & TMEM149 & 5.65 & 20 \\ 
ILMN\_1804396 & rs1293455 & rs2655991 & C14ORF4 & 1.38 & 7 \\ 
ILMN\_2313158 & rs10869600 & rs13069559 & MBNL1 & 3.15 & 15 \\ 
ILMN\_2372639 & rs17159840 & rs10059004 & TRAPPC5 & 4.17 & 17 \\ 
ILMN\_3231952 & rs12947580 & rs8079215 & ARL17B & 2.16 & 6 \\ 
   \hline
\end{tabular}
\caption*{This table shows the mean lambda per probe, when 5 or more interactions are identified amongst the 501 pairs}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllllllll}
  \hline
 probename & snp1 & snp2 & gene & chr1 & chr2 & lambda & P\_emp & P\_emp\_ferh & P\_emp\_egcut \\ 
  \hline
ILMN\_1652333 & rs898095 & rs9892064 & FN3KRP & 17 & 17 & 1.34 & 6.77 & 7.21 & 7.11 \\ 
ILMN\_1710752 & rs2123758 & rs3889129 & NAPRT1 & 8 & 8 & 2.14 & 7.36 & 7.42 & 6.99 \\ 
  ILMN\_1731043 & rs7776572 & rs11770192 & TRA2A & 7 & 7 & 1.36 & 6.84 & 4.19 & 3.67 \\ 
  ILMN\_1761797 & rs9979356 & rs3761385 & CSTB & 21 & 21 & 1.05 & 7.51 & 6.88 & 7.24 \\ 
  ILMN\_1769782 & rs1891432 & rs10900520 & LAX1 & 1 & 1 & 1.22 & 6.64 & 5.88 & 6.47 \\ 
  ILMN\_1786426 & rs807491 & rs7254601 & TMEM149 & 19 & 19 & 2.69 & 7.4 & 6.73 & 6.57 \\ 
  ILMN\_1795836 & rs9978658 & rs11701361 & C21ORF57 & 21 & 21 & 1.43 & 5.65 & 6.84 & 5.12 \\ 
  ILMN\_1799381 & rs2634462 & rs6486334 & SNORD14A & 11 & 11 & 2.45 & 7.22 & 6.63 & 6.82 \\ 
  ILMN\_2101920 & rs6894268 & rs4700810 & HNRPH1 & 5 & 5 & 1.47 & 7.14 & 6.59 & 7.43 \\ 
  ILMN\_2121437 & rs7563453 & rs4973397 & NCL & 2 & 2 & 1.2 & 5.88 & 5.87 & 5.96 \\ 
  ILMN\_2242463 & rs7930237 & rs556895 & CTSC & 11 & 11 & 1.12 & 5.59 & 7.21 & 6.34 \\ 
  ILMN\_2313158 & rs16864367 & rs13079208 & MBNL1 & 3 & 3 & 2.28 & 7.22 & 6.84 & 6.35 \\ 
  ILMN\_2358626 & rs2395095 & rs10824092 & ADK & 10 & 10 & 1.15 & 7.74 & 5.68 & 5.77 \\ 
  ILMN\_2398939 & rs8092433 & rs4890876 & MBP & 18 & 18 & 1.19 & 5.9 & 6.59 & 6.11 \\ 
  ILMN\_2410783 & rs11150847 & rs12602462 & GAA & 17 & 17 & 1.38 & 6.91 & 6.67 & 6.86 \\ 
   \hline
\end{tabular}
\caption*{Summary information for the pairs of SNPs that had permutation empirical $p<4.48^{-6}$. P\_emp ferh and egcut are the permutation empirical p-values corresponding to the f-statistics from the original replication}

\end{table}
\end{landscape}

Suggestions following discussions \\

1. Prediction \\
Of the 501 SNP pairs, 484 have both SNP in the EGCUT data. Most of the Inchianti SNPs need to be imputed, but we expect most to pass filtering. For pairs without and Inchianti SNP I propose using the SNP with the largest additive effect in the egcut data. \\

@@

2. New permutation \\

Explore a permutation analysis where $a+d$ for SNP1 and SNP2 are held constant. The suggestion was to permute the ''residual'' 4 df terms:

The model is: \\

$y_i=a1*xa1_i*xd1_i+a2*xa2_j+\left [ aa*xa1_i*x2a_i+...+dd*xd1_i*xd2_i \right ]+\epsilon $

with xa and xd indicator variables (dummies). I think that the suggestion was to permute the entire term in square brackets (say, $R_i$) across individuals, holding $y$ and the first 4 terms (dummies for $a$ and $d$) constant. An alternative is to permute each of the 4 residual terms across $y$ and $a+d$ dummies.
